---
title: "CCPDataModel"
author: "Bastian Reiter"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r calc, echo=FALSE}

library(dplyr)
library(dsCCPhos)

load("../Data/RealData/CCPTestData_A.RData")


tbl_BioSampling <- GetDFInfo(CCPTestData_A$BioSampling, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_Diagnosis <- GetDFInfo(CCPTestData_A$Diagnosis, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_Histology <- GetDFInfo(CCPTestData_A$Histology, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_Metastasis <- GetDFInfo(CCPTestData_A$Metastasis, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_MolecularDiagnostics <- GetDFInfo(CCPTestData_A$MolecularDiagnostics, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_Patient <- GetDFInfo(CCPTestData_A$Patient, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_Progress <- GetDFInfo(CCPTestData_A$Progress, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_RadiationTherapy <- GetDFInfo(CCPTestData_A$RadiationTherapy, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_Staging <- GetDFInfo(CCPTestData_A$Staging, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_Surgery <- GetDFInfo(CCPTestData_A$Surgery, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")

tbl_SystemicTherapy <- GetDFInfo(CCPTestData_A$SystemicTherapy, IncludeRandomExampleValues = TRUE) %>%
                      gt::gt(groupname_col = "DFName") %>%
                      TinkerLab::gtTheme_Tinker(TableWidth = "80%")



```



### BioSampling = sample

`r tbl_BioSampling`

### Diagnosis = sample

`r tbl_Diagnosis`

### Histology = sample

`r tbl_Histology`

### Metastasis = sample

`r tbl_Metastasis`

### MolecularDiagnostics = sample

`r tbl_MolecularDiagnostics`

### Patient = sample

`r tbl_Patient`

### Progress = sample

`r tbl_Progress`

### RadiationTherapy = sample

`r tbl_RadiationTherapy`

### Staging = sample

`r tbl_Staging`

### Surgery = sample

`r tbl_Surgery`

### SystemicTherapy = sample

`r tbl_SystemicTherapy`



