---
title: "Governance"
id: chapter-Governance
editor: source
---

```{r}
#| label: Setup
#| echo: false

knitr::opts_chunk$set(echo = FALSE)

source("RSetup.R", local = knitr::knit_global())
```

\

### Package Administration

**Bastian Reiter** \
[Goethe University Frankfurt\
University Hospital Frankfurt\
Department of Medicine\
Hematology and Medical Oncology]{style="font-size: 80%"}

**Daniel Maier** \
[German Cancer Research Center (DKFZ)\
German Cancer Consortium (DKTK)]{style="font-size: 80%"}


### Project Supervision

**Prof. Dr. Jörg Janne Vehreschild** \
[Goethe University Frankfurt\
University Hospital Frankfurt\
Department of Medicine\
Hematology and Medical Oncology]{style="font-size: 80%"}


### Research Associates

```{r}
#| label: ResearchAssociates

read_excel(path = "./files/Tables.xlsx", sheet = "ResearchAssociates") %>%
    select(Last_Name,
           First_Name,
           Primary_Affiliation,
           City,
           Author_Contributions) %>% 
    gt() %>%
    theme_gt_CDSG()
```


### Participating Institutions

```{r}
#| label: ParticipatingInstitutions

read_excel(path = "./files/Tables.xlsx", sheet = "ParticipatingSites") %>%
    gt() %>%
    theme_gt_CDSG(inp_TableAlign = "left")
```



### Funding



### Conflicts of Interest

We have no conflicts of interest to disclose.

