---
title: "Project Governance"
id: chapter-Governance
editor: source
---

```{r}
#| label: Setup
#| echo: false

knitr::opts_chunk$set(echo = FALSE)

source("RSetup.R", local = knitr::knit_global())
```

\

### Full Project Title

**Epidemiology and Inpatient Care Characteristics of HIV-positive Cancer Patients in German university hospitals: A Real World Data Exploration (HIVCAre).**

### Project Initiation

**Prof. Dr. Jörg Janne Vehreschild\
Melanie Stecher, PhD\
Stefanie Andreas, M.Sc.\
Dr. Daniel Maier**

### Project Supervision

**Prof. Dr. Jörg Janne Vehreschild** \
[Goethe University Frankfurt\
University Hospital Frankfurt\
Department of Medicine\
Hematology and Medical Oncology]{style="font-size: 80%"}

### Project Administration

**Bastian Reiter** \
[Goethe University Frankfurt\
University Hospital Frankfurt\
Department of Medicine\
Hematology and Medical Oncology]{style="font-size: 80%"}

### Research Associates

```{r}
#| label: ResearchAssociates

read_excel(path = "./files/Tables.xlsx", sheet = "ResearchAssociates") %>%
    select(Last_Name,
           First_Name,
           Primary_Affiliation,
           City,
           Author_Contributions) %>% 
    gt() %>%
    theme_gt_CDSG()
```

### Participating Institutions

```{r}
#| label: ParticipatingInstitutions

read_excel(path = "./files/Tables.xlsx", sheet = "ParticipatingSites") %>%
    gt() %>%
    theme_gt_CDSG(inp_TableAlign = "left")
```



### Funding

There is no third-party funding for this project.


### Conflicts of Interest

We have no conflicts of interest to disclose.


### Trial Registration

It is intended to register the study at the German Clinical Trial Register ([Deutsches Register Klinischer Studien, DRKS](https://www.bfarm.de/DE/Das-BfArM/Aufgaben/Deutsches-Register-Klinischer-Studien/_node.html?page=5)).


### Publication

The study results will be published in cooperation with all associates.
