---
title: "Limitations and Concerns"
id: chapter-LimitationsAndConcerns
editor: source
---
  
```{r}
#| label: Setup
#| echo: false

knitr::opts_chunk$set(echo = FALSE)

source("RSetup.R", local = knitr::knit_global())
```

\
The following chapter provides notes on **general limitations** (especially those that were identified at the time of Study Planning) and **detailed concerns** that occurred during analysis and may present potential origins of bias. All notes have been assigned to a level of estimated potential impact (Major, Medium, Minor).


### General / A-priori Limitations

```{r}
#| label: Limitations

read_excel(path = "./files/Tables.xlsx", sheet = "Limitations") %>%
    arrange(Estimated_Potential_Impact) %>%
    gt(groupname_col = "Estimated_Potential_Impact") %>%
    theme_gt_CDSG(inp_TableAlign = "left")
```


### Detailed Concerns

```{r}
#| label: Concerns

read_excel(path = "./files/Tables.xlsx", sheet = "Concerns") %>%
    arrange(Estimated_Potential_Impact) %>%
    gt(groupname_col = "Estimated_Potential_Impact") %>%
    theme_gt_CDSG(inp_TableAlign = "left")
```
