---
title: "Study Design"
id: chapter-StudyDesign
editor: source
---

```{r}
#| label: Setup
#| echo: false

knitr::opts_chunk$set(echo = FALSE)

source("RSetup.R", local = knitr::knit_global())
```


> **HIVCAre** is a multicenter retrospective cohort study, conducted on Real World Health Data from German university hospitals.


### Research Objectives    {#section-ResearchObjectives}

> **Main Objective:** Explore epidemiology and inpatient care characteristics of HIV-positive cancer patients

- Describe cancer occurrence in HIV-positive patients over time stratified by cancer category

- Explore possible differences in care characteristics between HIV-negative and HIV-positive cancer patients

- Explore differences in course of therapy between HIV-negative and HIV-positive cancer patients

For a detailed list of Research Items, see according Section [below](#section-ResearchItems).


### Study Data

The primary health data analyzed in this study is curated by hospitals following legal requirements founded in [ยง21 Krankenhausentgeltgesetz (KHEntgG)](https://www.gesetze-im-internet.de/khentgg/__21.html). For more details, see Chapter [Study Data](#chapter-StudyData).


### Study Cohort     {#section-StudyCohort}

Data of patients admitted to the following university hospitals (in alphabetical order):

```{r}
#| label: ParticipatingSites

read_excel(path = "./files/Tables.xlsx", sheet = "ParticipatingSites") %>%
    select(-Institution) %>%
    gt() %>%
    theme_gt_CDSG(inp_TableAlign = "left")
```

#### Inclusion criteria

-   Admitted between 01-01-2005 and 12-31-2022
-   Aged at least 18 years at date of admission
-   At least one documented ICD-10 code representing malignancy or HIV infection

#### Exclusion criteria

-   Implausible documentation of ICD-10 codes

\

#### Stratification Model

![](Images/StratificationModel){fig-alt="Stratification Model" fig-align="center"}

### Sample Size Determination

Since this study does not aim at a particular effect size analysis and it can be assumed that the yielded Sample Sizes will be rather large, no specific Sample Size Determination will be performed.
An estimation of the number of included patients will be available for each participating site and can reach up to 50.000 patients for large University hospitals.


### Research Items   {#section-ResearchItems}

The following research items result from the research objectives stated [here](#section-ResearchObjectives).

```{r}
#| label: ResearchItems

read_excel(path = "./files/Tables.xlsx", sheet = "ResearchItems") %>%
    gt(groupname_col = "Objective_Group") %>%
    theme_gt_CDSG()
```
